\chapter*{Acknowledgments}

This process has taken more from those around me than it ever could
have taken from me. From the moment my parents sent me to bed early
without letting me see the scanning electron microscope image of
molecules, I knew that I wanted to be a scientist. It was there
dedication to keeping me on the right path that lead to me to achieve
this. Thank you Mom for letting me be me and letting me play music and
trusting that I would still return to science (twice!!). Thank you Dad
for showing me what it means to be dedicated and not give up. Both of
you have given up a lot to see me to and through this process and it
is just as much your achievement as it is mine. My entire family has
done nothing but support me through this time in my life and for that
I am lucky and thankful

All the help I have had from the Gamma-ray Burst monitor team is
immeasurable. From the day I started I felt like I was part of a
family. thank you Michael Briggs from keeping me grounded and Valerie
Connaughton for being a great mentor and friend. Bill Paciesas and
Chip Meegan, thanks for your guidance. You guys are legends in this
field and it has been amazing to continue work that you paved the way
for so many years ago.

To my advisor, Rob Preece, thank you for taking a chance on a
graduated student in a desperate situation. Your guidence and
patience with my constant, daily diversion into some strange theory allowed
me to find a rewarding research topic. Though it will never be
communicated in beautiful English, I think we have accomplished some
great things and it is thanks to your help that they were able to be
written down. I will sincerely miss our chats about science and the
world.

I would be foolish to leave out George Clinton. Had I not stayed up
for five days straight with the pure sounds of extraterrestrial p-funk
keeping me going I would not have finished this work on time. It is
true that funk not only moves, it removes, dig?

Lastly, my son Isaac. You have sacrificed the most in all of this. You
came into the world helping me do quantum mechanics problems in the
middle of the night and spent the first parts of your life begging me
to close the books and play. I hope you will see those years as
something to learn from. Sometimes we have to sacrifice precious time
to do what is best for ourselves and those that depend on us. I look
forward to the day when you choose your path and work hard to become
what ever it is you believe in. I love you little buddy and thank you
for bearing with me all these years.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
